Testable normative theories

### 2020-05-20 simple.tex
Def \gargs to reduce to dynamic arguments that must be used

The set $\iPhi \subseteq \Phi$ is the set of interest. 
When $(\prop, \text{possible}) \in \iPhi$, $\prop$ is considered as a possibility in the deliberated judgment of $i$ (it is not rejected), and when $(\prop, \text{sure}) \in \iPhi$, $\prop$ is considered as a certainty in the deliberated judgment of $i$. 
Part of the content of $\Phi$ is known as a result of a correct normative and empirical analysis.

Given $\phi \in {\gleadsto}(\allargs)$, an argument $\ar \in \allargs$ is \emph{in favor of $\phi$}, $\ar \in \gargs[\phi, 1]$, iff $\ar \in [\gbeatsinv]^{2k}({\gleadstoinv}(\phi))$ for some $k \in \N$, where $R^\alpha$ denotes $\alpha$ times the composition of the relation $R$ with itself. (Throughout the article, $\N$ includes zero.)

Given $\phi \in {\gleadsto}(\allargs)$ and $1 ≤ k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + \gargs[\phi, 1] = \set{\ar_k + \ar_1 \suchthat \ar_k \in \gargs[\phi, k], \ar_1  \in \gargs[\phi, 1]}$. 
Define $\gargs[\phi] = \bigcup_{1 ≤ k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadstoinv}(\allargs)} \gargs[\phi]$.

Given $\phi \in \Phi$ and $\ar_0 \in \gargs[\phi]$, let $c^\phi(\ar_0) = \bigcup \set{\args \subseteq \gargs[\phi, 0] \suchthat \ar_0 = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar_0$ in favor of $\phi$.

@@

Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$. Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.

>>>>

Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \allargs$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$.

Given $\phi \in {\gleadsto}(\allargs)$, define $\gargs[\phi, 0] \subseteq \allargs$ as $\gargs[\phi, 0] = {\gleadstoinv}(\phi)$; and, for $k \in \N$, define $\gargs[\phi, k + 1] = \gargs[\phi, k] + [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k]) = \set{\ar_k + \ar \suchthat \ar_k \in \gargs[\phi, k], \ar  \in [{\gbeatsinv} \circ {\ibeatseinv[!\phi]}](\gargs[\phi, k])}$. (Throughout the article, $\N$ includes zero.) 
Define $\gargs[\phi] = \bigcup_{k \in \N} \gargs[\phi, k]$, and $\gargs = \cup_{\phi \in {\gleadsto}(\allargs)} \gargs[\phi]$.

Given $\ar \in \gargs$, let $c(\ar) = \bigcup \set{\args \subseteq \gargs \suchthat \ar = \sum \args} \subseteq \allargs$ denote the \emph{components} of $\ar$.

@@

\commentOC{TODO next: check $\gbeatsstar$ can be replaced. Then, comment that Bounded length does not imply finiteness of arguments used as counter-arguments by the model: model is able to counter infinitely many arguments with infinitely many counter-args, but needs to declare that an (unknown) finite subset of those will suffice to convince $i$.}
